Output Summary

### 2021-10-15 03-post-process/output-plots.Rmd
Update MCMC diagnostics for carcass correction coefficients

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
s_female = 1  # females are s = 1,
s_male   = 2  # males are s = 2
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3

# kso represents "age/sex/origin" combo
# e.g., kso = 1 is age 3 female NORs
# e.g., kso = 12 is age 5 male HORs
# these objects specify which elements of kso are for different aggregations of these
kso_age = list(
  kso_3 = c(1, 4, 7, 10),
  kso_4 = c(2, 5, 8, 11),
  kso_5 = c(3, 6, 9, 12)
)

kso_sex = list(
  kso_female = c(1,2,3,7,8,9),
  kso_male = c(4,5,6,10,11,12)
)

kso_origin = list(
  kso_nor = 1:6,
  kso_hor = 7:12
)
```

@@

```{r}
# Calculate hours per 10,000 iterations
hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
  # calculation of total iters differs if parallel or not
  if (parallel) {
    total_iters = n_adapt + n_post + n_burn
  } else {
    total_iters = (n_adapt + n_post + n_burn) * n_chains
  }
  ten_thousands_of_total_iters = total_iters/10000

@@

```{r mcmc-diag-function}
# a function to get MCMC diagnoses for a group of parameters
# params: a string to match with postpack::match_params()
# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
# L3: a "Level-3" group label; such as NOR or females or age-3 females

@@

# Sex Apportionment
L1 = "Sex Apportionment"
L2 = c("Mean", "Process SD", "Realized")
base = list("mu_omega[sex,origin,pop]", "sig_Lomega[origin,pop]", "omega[year,sex,origin,pop]")
match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
omega_diags = rbind(tmp1, tmp2)

# Probability of Maturing at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_psi_O1_Rb[sex,origin,pop]", "sig_Lpsi_O1_Rb[sex,origin,pop]", "psi_O1_Rb[.+,sex,origin,pop]")
match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
psi_O1_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)

# Probability of Maturing at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_psi_O2_Rb[sex,origin,pop]", "sig_Lpsi_O2_Rb[sex,origin,pop]", "psi_O2_Rb[.+,sex,origin,pop]")
match = sub_index(base, year = ".+", sex = s_female, origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (NOR)")))
match = sub_index(base, year = ".+", sex = s_female, origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Female (HOR)")))
match = sub_index(base, year = ".+", sex = s_male, origin = o_nor, pop = ".")
tmp3 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (NOR)")))
match = sub_index(base, year = ".+", sex = s_male, origin = o_hor, pop = ".")
tmp4 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "Male (HOR)")))
psi_O2_Rb_diags = rbind(tmp1, tmp2, tmp3, tmp4)

@@

# Year 3 ocean survival
L1 = "Year 3 Ocean Survival"
L2 = c("Mean")
base = c("mu_phi_O2_O3[origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".+")
phi_O2_O3_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Carcass Correction
L1 = "Carcass Correction Factor"
z_diags = diag_fn("z", L1 = L1)

@@

# Straying
L1 = "Strays"
L2 = c("Realized Number", "Age/Sex Comp")
match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = "."))
stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  omega_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_O2_O3_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

# primary containers: will store final recalculated output
q_Ra_age = q_Sa_adj_age = q_Ra_sex = q_Sa_adj_sex = q_Ra_origin = q_Sa_adj_origin = NULL

@@

  ## BY AGE, AGGREGATED ACROSS SEX AND ORIGIN

  # containers
  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,kso_age[[k]],j])
      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,kso_age[[k]],j])

@@

  ## BY SEX, AGGREGATED ACROSS AGE AND ORIGIN

  # containers
  q_Ra_sex_tmp = q_Sa_adj_sex_tmp = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
  inds_1_sex = inds_2_sex = inds_3_sex = q_Ra_sex_tmp
  for (j in 1:jags_data$nj) {
    for (s in 1:jags_data$ns) {
      # calculate aggregate proportions for each sex
      q_Ra_sex_tmp[,s,j] = rowSums(q_Ra[,kso_sex[[s]],j])
      q_Sa_adj_sex_tmp[,s,j] = rowSums(q_Sa_adj[,kso_sex[[s]],j])

      # build the element identifiers - for building names later
      inds_1_sex[,s,j] = 1:jags_data$ny
      inds_2_sex[,s,j] = s
      inds_3_sex[,s,j] = j
    }
  }

  # vectorize, add names, and remove NAs
  q_Ra_sex_v = as.numeric(q_Ra_sex_tmp)
  q_Sa_adj_sex_v = as.numeric(q_Sa_adj_sex_tmp)
  names(q_Ra_sex_v) = paste0("q_Ra_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
  names(q_Sa_adj_sex_v) = paste0("q_Sa_adj_sex[", as.numeric(inds_1_sex), ",", as.numeric(inds_2_sex), ",", as.numeric(inds_3_sex), "]")
  q_Ra_sex_v = q_Ra_sex_v[!is.na(q_Ra_sex_v)]
  q_Sa_adj_sex_v = q_Sa_adj_sex_v[!is.na(q_Sa_adj_sex_v)]

  ## BY ORIGIN, AGGREGATED ACROSS AGE AND SEX

  # containers
  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,kso_origin[[o]],j])
      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,kso_origin[[o]],j])

@@

  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
  q_Ra_sex = rbind(q_Ra_sex, q_Ra_sex_v)
  q_Sa_adj_sex = rbind(q_Sa_adj_sex, q_Sa_adj_sex_v)
  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)

@@

# combine new calculated quantites into a big matrix
q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_sex, q_Sa_adj_sex, q_Ra_origin, q_Sa_adj_origin)

@@

# these are the observed proportions by age (aggregated across sex and origin), sex (aggregated across age and origin), and origin (aggregated across age and sex)

# containers
x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
x_weir_sex_obs = x_carc_sex_obs = array(NA, dim = c(jags_data$ny, jags_data$ns, jags_data$nj))
x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,kso_age[[k]],j])
    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,kso_age[[k]],j])
  }

  # calculate aggregate proportions for each sex
  for (s in 1:jags_data$ns) {
    x_weir_sex_obs[,s,j] = rowSums(jags_data$weir_x_obs[,kso_sex[[s]],j])
    x_carc_sex_obs[,s,j] = rowSums(jags_data$carc_x_obs[,kso_sex[[s]],j])
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,kso_origin[[o]],j])
    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,kso_origin[[o]],j])
  }
}

dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_sex_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_sex_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]

x_weir_new_obs = list(
  x_weir_age_obs = x_weir_age_obs,
  x_weir_sex_obs = x_weir_sex_obs,
  x_weir_origin_obs = x_weir_origin_obs
)

x_carc_new_obs = list(
  x_carc_age_obs = x_carc_age_obs,
  x_carc_sex_obs = x_carc_sex_obs,
  x_carc_origin_obs = x_carc_origin_obs
)

@@

  par(mfcol = c(3,4), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Female\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Female\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Female\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Male\\,Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Male\\,Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Male\\,Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,7,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 7), main = TeX("$Female\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,8,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 8), main = TeX("$Female\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,9,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 9), main = TeX("$Female\\,Age\\,5\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,10,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 10), main = TeX("$Male\\,Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,11,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 11), main = TeX("$Male\\,Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,12,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 12), main = TeX("$Male\\,Age\\,5\\,(HOR)$"))

@@

# for fits to each age, aggregated across sexes and origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each sex, aggregated across ages and origins
weir_comp_fit_plot_sex = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))

  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 1), main = TeX("$Females$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_sex[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_sex_obs[observable,,j], 2), main = TeX("$Males$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages and sexes
weir_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))

@@

#### By Age/Sex/Origin {.tabset .tabset-pills}

@@

These figures show the agreement of the model with the weir composition data by age, aggregated by sex and origin.

@@

#### By Sex {.tabset .tabset-pills}

These figures show the agreement of the model with the weir composition data by sex, aggregated by age and origin.

```{r cat-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_cat)
```

```{r los-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_los)
```

```{r min-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_min)
```

```{r ugr-weir-comp-fit-sex, fig.width = 8, fig.height = 4}
weir_comp_fit_plot_sex(j_ugr)
```

@@

These figures show the agreement of the model with the weir composition data by origin, aggregated by age and sex.

@@

These figures show the number of samples gathered for age/sex/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

@@

#### By Age/Sex/Origin {.tabset .tabset-pills}

@@

These figures show the agreement of the model with the carcass composition data by age, aggregated by sex and origin.

@@

#### By Sex {.tabset .tabset-pills}

These figures show the agreement of the model with the carcass composition data by sex, aggregated by age and origin.

```{r cat-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_cat)
```

```{r los-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_los)
```

```{r min-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_min)
```

```{r ugr-carc-comp-fit-sex, fig.width = 8, fig.height = 4}
carc_comp_fit_plot_sex(j_ugr)
```

@@

These figures show the agreement of the model with the carcass composition data by origin, aggregated by age and sex.

@@

This figure illustrates that total spawners is a reasonable index of total egg production. The three lines illustrate the relationship if each spawner (regardless of age/sex) had a fixed number of eggs.

@@

The adult part is calculated across return years, by summing the number of adults of each age (regardless of sex) that return in the appropriate years. For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996. The calculation is done for hatchery and natural origin fish separately. Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.

@@

```{r stray-comp, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  x = post_summ(post, sub_index("stray_comp[age,sex,origin,pop]", age = ".", sex = ".", origin = o_hor, pop = j))

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "no-sex"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# dimension IDs
i_fall   = 1  # fall migrants are i = 1
i_spring = 2  # spring migrants are i = 2,
o_nor    = 1  # natural origin are o = 1,
o_hor    = 2  # hatchery origin are o = 2,
j_cat    = 1  # Catherine Creek is j = 1
j_los    = 2  # Lostine River is j = 2
j_min    = 3  # Minam River is j = 3
j_ugr    = 4  # Upper Grande Ronde River is j = 4
k_3      = 1  # age 3 is k = 1
k_4      = 2  # age 4 is k = 2
k_5      = 3  # age 5 is k = 3

# ko represents "age/origin" combo
# e.g., ko = 1 is age 3 NORs
# e.g., ko = 5 is age 4 HORs
# these objects specify which elements of ko are for different aggregations of these
ko_age = list(
  ko_3 = c(1, 4),
  ko_4 = c(2, 5),
  ko_5 = c(3, 6)
)

ko_origin = list(
  ko_nor = 1:3,
  ko_hor = 4:6
)
```

@@

```{r mcmc-time-info}
# Calculate hours per 10,000 iterations
hrs_per_ten_thousand_iters = with(model_info$jags_dims, {
  # calculation of total iters differs if parallel or not
  if (parallel) {
    total_iters = n_adapt + n_post + n_burn
  } else {
    total_iters = (n_adapt + n_post + n_burn) * n_chains
  }
  ten_thousands_of_total_iters = total_iters/10000

@@

```{r mcmc-diag-function}
# a function to get MCMC diagnoses for a group of parameters
# params: a string to match with postpack::match_params()
# L1: a "Level-1" group label; such as component of the model (e.g., LH apportionment)
# L2: a "Level-2" group label; such as type of parameter (e.g., mean, sd, or year-specific value)
# L3: a "Level-3" group label; such as NOR or HOR

@@

# Probability of Maturing at Age-3
L1 = "Pr(Mature at Age-3)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_psi_O1_Rb[origin,pop]", "sig_Lpsi_O1_Rb[origin,pop]", "psi_O1_Rb[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O1_Rb_diags = rbind(tmp1, tmp2)

# Probability of Maturing at Age-4
L1 = "Pr(Mature at Age-4)"
L2 = c("Mean", "Process SD", "Realized")
base = c("mu_psi_O2_Rb[origin,pop]", "sig_Lpsi_O2_Rb[origin,pop]", "psi_O2_Rb[.+,origin,pop]")
match = sub_index(base, year = ".+", origin = o_nor, pop = ".")
tmp1 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "NOR")))
match = sub_index(base, year = ".+", origin = o_hor, pop = ".")
tmp2 = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i], L3 = "HOR")))
psi_O2_Rb_diags = rbind(tmp1, tmp2)

@@

@@

# Carcass Correction
L1 = "Carcass Correction Factor"
L2 = c("Among-Pop Mean", "Among-Pop SD", "Pop-Specific")
match = c("mu_z[.]", "sig_z[.]", "^z[.,.]")
z_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

@@

# Straying
L1 = "Strays"
L2 = c("Realized Number", "Age Comp")
match = c("n_stray_tot[.+,.]", sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = "."))
stray_diags = unlist_dfs(lapply(1:length(match), function(i) diag_fn(match[i], L1 = L1, L2 = L2[i])))

# combine diagnostic summaries into one massive table
diags_table = rbind(
  parr_recruit_diags,
  pi_diags,
  phi_Pa_Mb_diags,
  phi_Mb_Ma_diags,
  phi_Ma_O0_diags,
  psi_O1_Rb_diags,
  psi_O2_Rb_diags,
  phi_O0_O1_diags,
  phi_O1_O2_diags,
  phi_Rb_Ra_diags,
  phi_Sb_Sa_diags,
  misc_ocean_surv_diags,
  z_diags,
  init_diags,
  stray_diags
)

@@

# primary containers: will store final recalculated output
q_Ra_age = q_Sa_adj_age = q_Ra_origin = q_Sa_adj_origin = NULL

@@

  ## BY AGE, AGGREGATED ACROSS ORIGINS

  # containers
  q_Ra_age_tmp = q_Sa_adj_age_tmp = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
  inds_1_age = inds_2_age = inds_3_age = q_Ra_age_tmp
  for (j in 1:jags_data$nj) {
    for (k in 1:jags_data$nk) {
      # calculate aggregate proportions for each age
      q_Ra_age_tmp[,k,j] = rowSums(q_Ra[,ko_age[[k]],j])
      q_Sa_adj_age_tmp[,k,j] = rowSums(q_Sa_adj[,ko_age[[k]],j])

@@

  ## BY ORIGIN, AGGREGATED ACROSS AGES

  # containers
  q_Ra_origin_tmp = q_Sa_adj_origin_tmp = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))
  inds_1_origin = inds_2_origin = inds_3_origin = q_Ra_origin_tmp
  for (j in 1:jags_data$nj) {
    for (o in 1:jags_data$no) {
      # calculate aggregate proportions for each origin
      q_Ra_origin_tmp[,o,j] = rowSums(q_Ra[,ko_origin[[o]],j])
      q_Sa_adj_origin_tmp[,o,j] = rowSums(q_Sa_adj[,ko_origin[[o]],j])

@@

  q_Ra_age = rbind(q_Ra_age, q_Ra_age_v)
  q_Sa_adj_age = rbind(q_Sa_adj_age, q_Sa_adj_age_v)
  q_Ra_origin = rbind(q_Ra_origin, q_Ra_origin_v)
  q_Sa_adj_origin = rbind(q_Sa_adj_origin, q_Sa_adj_origin_v)

@@

# combine new calculated quantities into a big matrix
q_new = cbind(q_Ra_age, q_Sa_adj_age, q_Ra_origin, q_Sa_adj_origin)

@@

# these are the observed proportions by age (aggregated across origins) and origin (aggregated across ages)

# containers
x_weir_age_obs = x_carc_age_obs = array(NA, dim = c(jags_data$ny, jags_data$nk, jags_data$nj))
x_weir_origin_obs = x_carc_origin_obs = array(NA, dim = c(jags_data$ny, jags_data$no, jags_data$nj))

for (j in 1:jags_data$nj) {
  # calculate aggregate proportions for each age
  for (k in 1:jags_data$nk) {
    x_weir_age_obs[,k,j] = rowSums(jags_data$weir_x_obs[,ko_age[[k]],j])
    x_carc_age_obs[,k,j] = rowSums(jags_data$carc_x_obs[,ko_age[[k]],j])
  }

  # calculate aggregate proportions for each origin
  for (o in 1:jags_data$no) {
    x_weir_origin_obs[,o,j] = rowSums(jags_data$weir_x_obs[,ko_origin[[o]],j])
    x_carc_origin_obs[,o,j] = rowSums(jags_data$carc_x_obs[,ko_origin[[o]],j])
  }
}

dimnames(x_weir_age_obs)[[1]] = dimnames(x_weir_origin_obs)[[1]] = dimnames(x_carc_age_obs)[[1]] = dimnames(x_carc_origin_obs)[[1]] = dimnames(jags_data$weir_x_obs)[[1]]

x_weir_new_obs = list(
  x_weir_age_obs = x_weir_age_obs,
  x_weir_origin_obs = x_weir_origin_obs
)

x_carc_new_obs = list(
  x_carc_age_obs = x_carc_age_obs,
  x_carc_origin_obs = x_carc_origin_obs
)

@@

  par(mfrow = c(2,3), oma = c(1.5,1.5,0,0))#, mar = c(1.5,1.5,1.5,0.5))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 1), main = TeX("$Age\\,3\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 2), main = TeX("$Age\\,4\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 3), main = TeX("$Age\\,5\\,(NOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,4,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 4), main = TeX("$Age\\,3\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,5,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 5), main = TeX("$Age\\,4\\,(HOR)$"))
  plot_tseries(post_summ(post, sub_index("^q_Ra[.+,6,pop]$", pop = j)), get_obs_ests_multinomial(jags_data$weir_x_obs[observable,,j], 6), main = TeX("$Age\\,5\\,(HOR)$"))

@@

# for fits to each age, aggregated across origins
weir_comp_fit_plot_age = function(j) {
  par(mfcol = c(1,3), oma = c(1.5,1.5,0,0))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,1,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 1), main = TeX("$Age\\,3$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,2,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 2), main = TeX("$Age\\,4$"), ylim = c(0,1))
  plot_tseries(post_summ(post, sub_index("^q_Ra_age[.+,3,pop]$", pop = j)), get_obs_ests_multinomial(x_weir_new_obs$x_weir_age_obs[observable,,j], 3), main = TeX("$Age\\,5$"), ylim = c(0,1))
  mtext(side = 1, outer = T, line = 0.25, "Return Year")
  mtext(side = 2, outer = T, line = 0.25, "Proportion of Return")
}

# for fits to each origin, aggregated across ages
weir_comp_fit_plot_origin = function(j) {
  par(mfcol = c(1,2), oma = c(1.5,1.5,0,0))

@@

#### By Age/Origin {.tabset .tabset-pills}

This is the resolution the model fits to: each year slice is treated as a 6-element multinomial vector.

@@

These figures show the agreement of the model with the weir composition data by age, aggregated across origins.

@@

@@

These figures show the agreement of the model with the weir composition data by origin, aggregated across ages.

@@

These figures show the number of samples gathered for age/origin composition information during carcass surveys. The model will fit more closely to years with more samples.

@@

#### By Age/Origin {.tabset .tabset-pills}

@@

These figures show the agreement of the model with the carcass composition data by age, aggregated across origins.

@@

@@

These figures show the agreement of the model with the carcass composition data by origin, aggregated across ages.

@@

This figure illustrates that total spawners is a reasonable index of total egg production, according to the assumptions of our model. The three lines illustrate the relationship if each spawner (regardless of age or sex) had a fixed number of eggs.

@@

The adult part is calculated across return years, by summing the number of adults of each age that return in the appropriate years. For example, the SAR for brood year 1991 uses smolt that were spawned in 1991, out-migrated in spring 1993, divided by the sum of age 3 adults in 1994, age 4 adults in 1995, and age 5 adults in 1996. The calculation is done for hatchery and natural origin fish separately. Only SARs through brood year 2014 are calculated, since this is the last year of complete adult returns.

@@

```{r stray-comp, fig.width = 6, fig.height = 5}
plot_fn = function(j) {
  x = post_summ(post, sub_index("stray_comp[age,origin,pop]", age = ".", origin = o_hor, pop = j))

  par(mar = c(5,2,1,1), tcl = -0.15, mgp = c(2, 0.35, 0))
  mp = barplot(x["mean",], ylim = c(0, 1), xaxt = "n", main = pops[j], col = alpha("salmon", 0.5), border = alpha("red", 0.5))
  segments(mp, x["2.5%",], mp, x["97.5%",], col = alpha("red", 0.5))
  axis(side = 1, at = mp, labels = paste0("Age", jags_data$kmin:jags_data$kmax), las = 2)
  segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE)
}

par(mfrow = c(2,2), oma = c(0,1.5,0,0))
junk = sapply(1:jags_data$nj, plot_fn)
mtext(side = 2, outer = T, line = 0.25, "Proportion of Strays by Age")
```
